\Title

### 2022-09-27 Grimaldi-etal-BiolCybernetics.tex
Introduction: 1.2.a

\subsection{What can neuroscience bring to computer vision?}% and the Hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------
% 1.2.a

>>>>

\subsection{What can neuroscience bring to computer vision?}% and the Hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------
% 1.2.a
Let's focus first on some existing
spiking neural network models. one
first motivation for these models was
to understand the biological observations
at different scales. For instance the Hodgkin
Huxley mode describes the 'dynamic
of the membrane potential and the role
of the different voltage-gated ion channels. It
also explains how the all may emit
a spike. Larger scale models introduce
an explicit spiking mechanism, for
instance in the Integrate-and-Fine
model which allows to predict the
emerging states of a network of recurrently
connected neurons (Brunel). Several
models have sealed up the system to
include more neurons such as the
Virtual Brain (Sanz) which allows
to mix spiking neural nets with
analog neural mass models. However
these methods are merely descriptive
and have application in neuroscience
and few have had an impact in
computer vision.

Another class of attempts have designed
spiking neural networks that aim to
have applications in machine learning.
One of these is the Spike Nap algorithm
which uses a radical approach by
anding information using one spite
per nen non :(Delorme). Another branch
of spiking neural networks attempt
to determine the structure of the
network such as to minimize a cot
function. This has been implemented
in the Spike Prop algorithm (Bonte)
and is now widely used in methods
Trying to transfer the performance
of CNN s to Sn Ns, for instance by
using a surrogate gradient approach.
However, the performance of SNN always
fall short of that of analog networks
and the question of the advantage of
using spin is still open.
A novel
generation of algorithms has
emerged with so-called silicon retina
which mimi de the output of the retina,
by representing the information using
espibes. one of this approach is that
of Lagorce, which uses the time
to the last spike to encode information in
in so-called temporal surfaces. We
have recently extended this Mots
algorithm to provide with an online
response and shown near-son -
performances on categwitha notable more
energy-efficient budget. A naige
of similar algorithms are applied
to real-life applications like optic
flow (Benotman), depth estimation
(Dandelot) on Gesture-Recently such
algorithm was used in the space
industry which is famous for its stringeant
selection process.
